Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural Morphemes

### 2019-01-29 Paper/AgreementAttraction.Rmd

- affilnum: 1
  affil: Bogazici University, South Campus, John Freely Building, Department of Linguistics, 34342, Istanbul, Turkey

@@

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: yes
spacing: singlespacing
footerdate: yes
bibliography: 
  - references.bib
  - knitcitations.bib
csl: ecology.csl

>>>>

- affilnum: 1
  affil: Bogazici University, Department of Linguistics, Istanbul, Turkey

@@

documentclass: article
classoption: a4paper
capsize: normalsize
fontsize: 11pt
geometry: margin=1in
linenumbers: no
spacing: singlespacing
footerdate: yes
bibliography: 
  - references.bib
  - knitcitations.bib
csl: ecology.csl

### 2019-01-29 Paper/AgreementAttraction.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Changes borrowed from @cboettig, added by @jhollist 
% A modified page layout 
\textwidth 6.75in
\oddsidemargin -0.15in
\evensidemargin -0.15in
\textheight 9in
\topmargin -0.5in
\usepackage{lineno} % add 
  \linenumbers % turns line numbering on 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural
Morphemes
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Utku Turk \textsuperscript{*} \textsuperscript{1} 
Pavel Logacev \textsuperscript{1} 
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}Bogazici University, South Campus, John Freely Building, Department of
Linguistics, 34342, Istanbul, Turkey\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:utku.turk@boun.edu.tr}{\nolinkurl{utku.turk@boun.edu.tr}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

@@

\hypertarget{introduction}{%
\section{INTRODUCTION}\label{introduction}}

@@

\hypertarget{replicaton-of-lago-et-al.-2018}{%
\section{REPLICATON OF LAGO ET AL.
(2018)}\label{replicaton-of-lago-et-al.-2018}}

@@

\hypertarget{participants-and-procedure}{%
\subsection{Participants and
Procedure}\label{participants-and-procedure}}

@@

\hypertarget{results-and-discussion}{%
\subsection{Results and Discussion}\label{results-and-discussion}}

@@

\hypertarget{experiment-2-rc-attractor}{%
\section{EXPERIMENT 2: RC ATTRACTOR}\label{experiment-2-rc-attractor}}

@@

\hypertarget{materials}{%
\subsection{Materials}\label{materials}}

@@

\hypertarget{participants-and-procedure-1}{%
\subsection{Participants and
Procedure}\label{participants-and-procedure-1}}

@@

\hypertarget{expectations}{%
\subsection{Expectations}\label{expectations}}

@@

Our objective is to explore the number attraction phenomenon without the
effects of case information and without the limits of nominal paradigm.
By doing so, we expect participants to engage with the sentences which
are ungrammatical in an extremely shallow fashion. We argue that instead
of reconstructing the sentence utilizing every detail from the attractor
and the controller, participants disregard the information from other
sources in the sentence and look for a matching morpheme,
i.e.~\emph{-lAr}.

@@

\hypertarget{discussion}{%
\section{DISCUSSION}\label{discussion}}

@@

\hypertarget{conclusions}{%
\section{CONCLUSIONS}\label{conclusions}}

@@

\hypertarget{acknowledgements}{%
\section{ACKNOWLEDGEMENTS}\label{acknowledgements}}

@@

\hypertarget{references}{%
\section{REFERENCES}\label{references}}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Allaire_2018}{}%
Allaire, J., Y. Xie, J. McPherson, J. Luraschi, K. Ushey, A. Atkins, H.
Wickham, J. Cheng, W. Chang, and R. Iannone. 2018. Rmarkdown: Dynamic
documents for r.

\leavevmode\hypertarget{ref-Lago}{}%
Lago, S. 2018. Straight from the horse's mouth: agreement attraction
effects with Turkish possessors.

\leavevmode\hypertarget{ref-R_Core_Team_2018}{}%
R Core Team. 2018. R: A language and environment for statistical
computing. R Foundation for Statistical Computing, Vienna, Austria.

\leavevmode\hypertarget{ref-Wagers2009}{}%
Wagers, M. W., E. F. Lau, and C. Phillips. 2009. Agreement attraction in
comprehension: Representations and processes. Journal of Memory and
Language 61:206--237.

\leavevmode\hypertarget{ref-Wickham_2016}{}%
Wickham, H. 2016. Ggplot2: Elegant graphics for data analysis.
Springer-Verlag New York.

\leavevmode\hypertarget{ref-woolford}{}%
Woolford, E. 2009. Differential subject marking at argument structure,
syntax, and pf. Pages 17--40 \emph{in} Differential subject marking.
Springer.

\leavevmode\hypertarget{ref-Xie_2014}{}%
Xie, Y. 2014. Knitr: A comprehensive tool for reproducible research in
R. \emph{in} V. Stodden, F. Leisch, and R. D. Peng, editors.
Implementing reproducible computational research. Chapman; Hall/CRC.

\leavevmode\hypertarget{ref-Xie_2015}{}%
Xie, Y. 2015. Dynamic documents with R and knitr. 2nd editions. Chapman;
Hall/CRC, Boca Raton, Florida.

\leavevmode\hypertarget{ref-Xie_2018}{}%
Xie, Y. 2018. Knitr: A general-purpose package for dynamic report
generation in r.

\leavevmode\hypertarget{ref-Xie_2018a}{}%
Xie, Y., J. Allaire, and G. Grolemund. 2018. R markdown: The definitive
guide. Chapman; Hall/CRC, Boca Raton, Florida.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Changes borrowed from @cboettig, added by @jhollist 
% A modified page layout 
\textwidth 6.75in
\oddsidemargin -0.15in
\evensidemargin -0.15in
\textheight 9in
\topmargin -0.5in
\usepackage{lineno} % add 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge Agreement Attraction in Turkish: Effects of Nominal and Verbal Plural
Morphemes
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Utku Turk \textsuperscript{*} \textsuperscript{1} 
Pavel Logacev \textsuperscript{1} 
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}Bogazici University, Department of Linguistics, Istanbul, Turkey\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:utku.turk@boun.edu.tr}{\nolinkurl{utku.turk@boun.edu.tr}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

@@

\section{INTRODUCTION}\label{introduction}

@@

\section{REPLICATON OF LAGO ET AL.
(2018)}\label{replicaton-of-lago-et-al.-2018}

@@

\subsection{Participants and
Procedure}\label{participants-and-procedure}

@@

\subsection{Results and Discussion}\label{results-and-discussion}

@@

\section{EXPERIMENT 2: RC ATTRACTOR}\label{experiment-2-rc-attractor}

@@

\subsection{Materials}\label{materials}

@@

\subsection{Participants and
Procedure}\label{participants-and-procedure-1}

@@

\subsection{Expectations}\label{expectations}

@@

Our objective is to explore the number attraction phenomenon without the
effects of case information and without the limits of nominal paradigm.
By doing so, we expect participants to engage with the sentences which
are ungrammatical in an extremely shallow fashion. We argue that instead
of reconstructing the sentence utilizing every detail from the attractor
and the controller, participants disregard the information from other
sources in the sentence and look for a matching morpheme, i.e.
\emph{-lAr}.

@@

\section{DISCUSSION}\label{discussion}

@@

\section{CONCLUSIONS}\label{conclusions}

@@

\section{ACKNOWLEDGEMENTS}\label{acknowledgements}

@@

\section{REFERENCES}\label{references}

\hypertarget{refs}{}
\hypertarget{ref-Allaire_2018}{}
Allaire, J., Y. Xie, J. McPherson, J. Luraschi, K. Ushey, A. Atkins, H.
Wickham, J. Cheng, W. Chang, and R. Iannone. 2018. Rmarkdown: Dynamic
documents for r.

\hypertarget{ref-Lago}{}
Lago, S. 2018. Straight from the horse's mouth: agreement attraction
effects with Turkish possessors.

\hypertarget{ref-R_Core_Team_2018}{}
R Core Team. 2018. R: A language and environment for statistical
computing. R Foundation for Statistical Computing, Vienna, Austria.

\hypertarget{ref-Wagers2009}{}
Wagers, M. W., E. F. Lau, and C. Phillips. 2009. Agreement attraction in
comprehension: Representations and processes. Journal of Memory and
Language 61:206--237.

\hypertarget{ref-Wickham_2016}{}
Wickham, H. 2016. Ggplot2: Elegant graphics for data analysis.
Springer-Verlag New York.

\hypertarget{ref-woolford}{}
Woolford, E. 2009. Differential subject marking at argument structure,
syntax, and pf. Pages 17--40 \emph{in} Differential subject marking.
Springer.

\hypertarget{ref-Xie_2014}{}
Xie, Y. 2014. Knitr: A comprehensive tool for reproducible research in
R. \emph{in} V. Stodden, F. Leisch, and R. D. Peng, editors.
Implementing reproducible computational research. Chapman; Hall/CRC.

\hypertarget{ref-Xie_2015}{}
Xie, Y. 2015. Dynamic documents with R and knitr. 2nd editions. Chapman;
Hall/CRC, Boca Raton, Florida.

\hypertarget{ref-Xie_2018}{}
Xie, Y. 2018. Knitr: A general-purpose package for dynamic report
generation in r.

\hypertarget{ref-Xie_2018a}{}
Xie, Y., J. Allaire, and G. Grolemund. 2018. R markdown: The definitive
guide. Chapman; Hall/CRC, Boca Raton, Florida.
